The \dealii Library, Version 9.2

### 2020-05-13 9.2/paper.tex
Expand on a comment.

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. A particular example is that we have
converted a number of programs to use range-based for loops (a C++11
feature) for loops over a range of integer indices, given that the
range-based way of writing loops seems to be the idiomatic approach
these days.

>>>>

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. A particular example is that we have
converted a number of programs to use range-based for loops (a C++11
feature) for loops over a range of integer indices such as loops over
all quadrature points or all indices of degrees of freedom during
assembly. This makes sense given that the
range-based way of writing loops seems to be the idiomatic approach
these days, and that we had previously already converted loops over
all cells in this way.
